\documentclass[12pt,a4paper,oneside]{report}

% ===== Packages =====
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{array}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{longtable}
\usepackage{multirow}

% ===== Colors =====
\definecolor{}{RGB}{220,20,60}
\definecolor{darkred}{RGB}{178,34,34}
\definecolor{lightgray}{RGB}{245,245,245}

% ===== Header/Footer =====
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{}{\textbf{}}}
\fancyhead[R]{\nouppercase{\rightmark}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{2pt}
\renewcommand{\headrule}{
  \color{}\hrule width\headwidth height\headrulewidth \kern-\headrulewidth
}

% ===== Section Formatting =====
\titleformat{\chapter}[hang]{\Huge\bfseries\color{darkred}}{Chapter \thechapter:}{0.5em}{\Huge\bfseries}
\titleformat{\section}[hang]{\Large\bfseries\color{}}{}{0em}{\Large\bfseries}
\titleformat{\subsection}[hang]{\large\bfseries\color{darkred}}{}{0em}{\large\bfseries}

\onehalfspacing

\begin{document}

% ================= TITLE PAGE ===================
\begin{titlepage}
    \centering
    \vspace*{3cm}
    {\Huge\bfseries\color{DonorFlow} DonorFlow}\\[0.7cm]
    {\Large\bfseries Blood Donation App with Gamified Rewards \& Community Impact}\\[2cm]

    {\Large\textbf{Mobile Development Project}}\\[0.5cm]
    {\large Academic Year 2025}\\[2cm]

    {\Large\textbf{Team Members}}\\[0.3cm]
    \large
    \begin{tabular}{l}
        Mechouahi Riffi Aya \\
        El Fakir Hassane \\
    \end{tabular}
    \\[2.5cm]

    {\large Version: 1.0}\\
    {\large Project Duration: 3 Weeks}\\[3cm]

    \vfill
\end{titlepage}

\tableofcontents
\newpage

% ================= CHAPTER 1 ===================
\chapter{Project Overview}

\section{App Title}
\textbf{DonorFlow} – Where Giving Blood Becomes Your Greatest Achievement

\section{Short Description}
 is an Android mobile app designed to encourage and streamline blood donation using gamification and community engagement.  
Users can schedule appointments, track donation history, earn badges, redeem points, and engage with leaderboards.

The goal is to increase donor retention by making the blood donation process rewarding, simple, and impactful.

\section{Target Users}

\subsection*{Primary Users}
\begin{itemize}
    \item Blood donors aged 18–65
    \item Students and young adults
    \item Users interested in health, volunteering, or gamification
\end{itemize}

\subsection*{Secondary Users}
\begin{itemize}
    \item Blood donation organizers
    \item Hospitals and health institutions
    \item Partner merchants
\end{itemize}



% ================= CHAPTER 2 ===================
\chapter{Functional Requirements}

\section{Core Features}

\subsection*{FR\#1: User Authentication \& Profile Setup}
\textbf{Description:} Users can create an account using email/password or social login. They set up their profile with name, blood type, location, and contact details. The system securely stores credentials and allows users to log in on subsequent app launches.\\
\textbf{Priority:} \textit{Must-have}

\subsection*{FR\#2: Search \& View Nearby Donation Campaigns}
\textbf{Description:} Users can search for nearby blood donation drives using location services or manual address input. The app displays a list and map view of available campaigns with details like date, time, location, and blood types needed.\\
\textbf{Priority:} \textit{Must-have}

\subsection*{FR\#3: Book and Manage Appointments}
\textbf{Description:} Users can book appointments for specific donation campaigns by selecting a time slot. They can view upcoming appointments, receive confirmation, and cancel or reschedule if needed. Appointment details are saved in their profile.\\
\textbf{Priority:} \textit{Must-have}

\subsection*{FR\#4: Achievement Badges}
\textbf{Description:} Users earn badges for completing specific milestones (e.g., first donation, 5 donations, completing profile). Badges are displayed on the profile and provide visual recognition of achievement. Each badge has a name, icon, and unlock criteria.\\
\textbf{Priority:} \textit{Must-have}

\subsection*{FR\#5: Points System}
\textbf{Description:} Users accumulate points for each donation completed. Points are displayed on the profile and contribute to leaderboard rankings. The system tracks total points earned and can be extended in future versions to redeem rewards.\\
\textbf{Priority:} \textit{Must-have}

\subsection*{FR\#6: Donation History \& Stats}
\textbf{Description:} Users can view a complete history of their past donations including date, location, and blood type donated. Statistics show total donations, points earned, and impact metrics. This feature helps users track their contribution over time.\\
\textbf{Priority:} \textit{Must-have}

\subsection*{FR\#7: Leaderboard}
\textbf{Description:} A simplified leaderboard displays top donors based on points earned. Users can see their ranking and compare with others in the community. This encourages friendly competition and motivates continued participation.\\
\textbf{Priority:} \textit{Nice-to-have}

\subsection*{FR\#8: Push Notifications}
\textbf{Description:} Users receive notifications for upcoming appointments, new donation campaigns nearby, achievement unlocks, and motivational reminders. Notifications can be customized in settings to control frequency and types.\\
\textbf{Priority:} \textit{Nice-to-have}

% ================= CHAPTER 3 ===================
\chapter{Non-Functional Requirements}

\section{NFR\#1: Usability and Intuitive Navigation}
The app must provide a simple, clean, and intuitive user interface that follows Material Design 3 guidelines. Navigation between screens should be logical and consistent. Users with minimal technical experience should be able to book an appointment within 3 taps from the home screen. Clear visual hierarchy and familiar UI patterns ensure users can accomplish tasks without confusion.

\section{NFR\#2: Performance and Responsiveness}
The app must load the main home screen within 2 seconds of launch on mid-range Android devices. Map rendering for nearby campaigns should complete within 3 seconds. All user interactions (button presses, screen transitions) must respond within 500ms to maintain a smooth experience. The app should not freeze or become unresponsive during normal operations.

\section{NFR\#3: Error Handling and Input Validation}
The app must handle invalid user input gracefully by displaying clear error messages. Form validation should occur in real-time (e.g., invalid email format, missing required fields). Network errors should be caught and displayed with retry options. The app should not crash when encountering unexpected data or connectivity issues.

\section{NFR\#4: Reliability and Data Persistence}
The app must reliably cache user profile data, donation history, and appointment details locally using SQLite. This ensures users can view their past donations even without internet connectivity. The app should synchronize data with the cloud backend when connectivity is restored.

\section{NFR\#5: Consistent Behavior in Portrait Orientation}
The app is designed to work consistently in portrait orientation. All screens must display correctly and maintain proper layout in portrait mode. While landscape support is not required for the MVP, the UI should not break if the device rotates temporarily.

% ================= CHAPTER 4 ===================
\chapter{Screens and Navigation}

\section{Screen Descriptions}

\subsection*{Screen 1: Splash Screen}
\textbf{Purpose:} Display app logo and branding while initializing the application.\\
\textbf{Main UI Components:} App logo, app name, loading indicator.\\
\textbf{User Actions:} None (auto-transitions after 2-3 seconds).\\
\textbf{Navigation:} Automatically navigates to Login Screen if user is not authenticated, or to Home Dashboard if user is already logged in.

\subsection*{Screen 2: Login / Sign-Up Screen}
\textbf{Purpose:} Allow users to authenticate or create a new account.\\
\textbf{Main UI Components:} Email text field, password text field, login button, sign-up link, social login buttons (optional), forgot password link.\\
\textbf{User Actions:} Enter credentials and log in, tap sign-up to create new account, use social login options.\\
\textbf{Navigation:} From Splash Screen. After successful login, navigates to Home Dashboard. Sign-up link navigates to Profile Setup Screen.

\subsection*{Screen 3: Home Dashboard}
\textbf{Purpose:} Serve as the main hub displaying user stats, upcoming appointments, and quick access to key features.\\
\textbf{Main UI Components:} Welcome message, total donations count, points balance, upcoming appointment card, quick action buttons (Find Campaigns, View History, Achievements), navigation bar.\\
\textbf{User Actions:} View summary statistics, navigate to other main screens via bottom navigation or action buttons.\\
\textbf{Navigation:} From Login Screen. User can navigate to Search Campaigns, Donation History, Achievements, Leaderboard, or Profile screens.

\subsection*{Screen 4: Search Donation Campaigns}
\textbf{Purpose:} Display available blood donation campaigns near the user's location.\\
\textbf{Main UI Components:} Search bar, location filter, map view toggle, list of campaigns (each showing name, date, location, distance), campaign cards with details.\\
\textbf{User Actions:} Search by location, view campaigns on map or list, tap on a campaign to view details, filter by blood type or date.\\
\textbf{Navigation:} From Home Dashboard. Tapping a campaign navigates to Campaign Details Screen, which leads to Appointment Booking.

\subsection*{Screen 5: Appointment Booking Screen}
\textbf{Purpose:} Allow users to book an appointment for a specific donation campaign.\\
\textbf{Main UI Components:} Campaign details (name, location, date), available time slots, date picker, confirm booking button, cancel button.\\
\textbf{User Actions:} Select preferred date and time slot, confirm booking, cancel and return to previous screen.\\
\textbf{Navigation:} From Search Donation Campaigns or Campaign Details Screen. After booking, returns to Home Dashboard with confirmation message.

\subsection*{Screen 6: Donation History Screen}
\textbf{Purpose:} Display a chronological list of the user's past donations.\\
\textbf{Main UI Components:} List of donation records (each showing date, location, blood type), total donations count, total points earned, filter options.\\
\textbf{User Actions:} Scroll through history, view details of individual donations, filter by date range.\\
\textbf{Navigation:} From Home Dashboard via navigation bar. User can return to Home or navigate to other main screens.

\subsection*{Screen 7: Achievements Screen}
\textbf{Purpose:} Display earned and locked badges that motivate users.\\
\textbf{Main UI Components:} Grid of badge icons, badge names, unlock criteria descriptions, progress indicators for locked badges.\\
\textbf{User Actions:} View earned badges, see requirements for locked badges, share achievements (optional).\\
\textbf{Navigation:} From Home Dashboard. User can return to Home or navigate to other main screens.

\subsection*{Screen 8: Leaderboard Screen}
\textbf{Purpose:} Show rankings of top donors in the community.\\
\textbf{Main UI Components:} Ranked list of donors (username, points, rank), user's current position highlighted, filter options (weekly, monthly, all-time).\\
\textbf{User Actions:} View rankings, see their own position, scroll through top donors.\\
\textbf{Navigation:} From Home Dashboard via navigation bar. User can return to Home or navigate to other main screens.

\subsection*{Screen 9: Profile \& Settings Screen}
\textbf{Purpose:} Display user information and allow account management.\\
\textbf{Main UI Components:} Profile picture, name, blood type, contact info, edit profile button, notification settings toggle, logout button.\\
\textbf{User Actions:} Edit profile information, adjust notification preferences, log out of account.\\
\textbf{Navigation:} From Home Dashboard via navigation bar. Edit profile opens Profile Edit Screen. Logout returns to Login Screen.

% ================= CHAPTER 5 ===================
\chapter{Technical Architecture}

\section{Local Storage}
SQLite for caching donation history, badges, and user session.

\section{Cloud Backend (Lightweight)}
Firebase Authentication + Firebase Firestore for user info, donation drives, and points.

\section{APIs}
\begin{itemize}
    \item Google Maps API  
    \item Mock Blood Campaign Data API  
\end{itemize}

% ================= CHAPTER 6 ===================
\chapter{Work Distribution and Project Plan}

\section{Timeline and Milestones}

The project is divided into three distinct phases over a three-week period:

\subsection*{Week 1 — Planning, Design, and Tool Selection}
\textbf{Milestones:}
\begin{itemize}
    \item Complete project conception and requirement analysis
    \item Design wireframes for all major screens (hand-drawn or digital)
    \item Finalize UI/UX design decisions and visual style
    \item Research and select development tools, libraries, and frameworks:
    \begin{itemize}
        \item Android Studio with Kotlin
        \item Firebase Authentication and Firestore
        \item Google Maps API
        \item SQLite for local storage
        \item Material Design 3 components
    \end{itemize}
    \item Set up development environment and project structure
    \item Begin initial implementation: UI skeleton and navigation framework
\end{itemize}

\subsection*{Week 2 — Development and Implementation}
\textbf{Milestones:}
\begin{itemize}
    \item Implement all core features:
    \begin{itemize}
        \item User authentication and profile management
        \item Search and view donation campaigns
        \item Appointment booking functionality
        \item Badge achievement system
        \item Points tracking system
        \item Donation history and statistics
    \end{itemize}
    \item Integrate Firebase backend and Google Maps API
    \item Implement local data caching with SQLite
    \item Complete all navigation flows between screens
    \item Implement optional features if time permits (leaderboard, notifications)
\end{itemize}

\subsection*{Week 3 — Testing, Finalization, and Polishing}
\textbf{Milestones:}
\begin{itemize}
    \item Comprehensive testing of all features and user flows
    \item Bug fixing and error handling improvements
    \item UI/UX refinements and visual polish
    \item Performance optimization
    \item Final integration testing
    \item Prepare project documentation and demonstration
    \item Finalize the app for submission
\end{itemize}

\section{Responsibilities}

\textbf{Student A (Aya):}
\begin{itemize}
    \item Week 1: Create wireframes, design UI mockups, set up navigation structure
    \item Week 2: Implement UI components, appointment booking, badge system
    \item Week 3: UI polishing, notification system, usability testing
\end{itemize}

\textbf{Student B (Hassane):}
\begin{itemize}
    \item Week 1: Research and configure development tools, set up Firebase backend
    \item Week 2: Implement authentication, search/campaigns API, points system, leaderboard
    \item Week 3: Backend integration testing, data persistence, bug fixes
\end{itemize}

\textbf{Shared Responsibilities:}
\begin{itemize}
    \item Week 1: Project planning, requirement documentation
    \item Week 2: Donation history feature, feature integration
    \item Week 3: Final testing, documentation, project presentation preparation
\end{itemize}

% ================= CHAPTER 7 ===================
\chapter{Success Metrics}
\begin{itemize}
    \item Smooth login and booking flow  
    \item At least 6 working screens  
    \item Badges unlock correctly  
    \item Points system working  
    \item Leaderboard updates  
    \item No critical crashes  
\end{itemize}

\end{document}
